\partchapter{Self Awareness}{I}

\lettrine{“A}{bbott}, Hannah!''

\quad\quad
Pause.

"HUFFLEPUFF!"

"Bones, Susan!"

Pause.

"HUFFLEPUFF!"

"Boot, Terry!"

Pause.

"RAVENCLAW!"

Harry glanced over briefly at his new House-mate, more to get a quick look at
the face than anything else. He was still trying to get himself under control
from his encounter with the ghosts. The sad, the really sad, the really truly
sad thing was that he \emph{did} seem to be getting himself under control
again. It seemed ill-fitting. Like he should have taken at least a day. Maybe a
whole lifetime. Maybe just never.

"Corner, Michael!"

Long pause.

"RAVENCLAW!"

At the lectern before the huge Head Table stood Professor McGonagall, looking
sharp and looking sharply around, as she called out one name after another,
though she had smiled only for Hermione and a few others. Behind her, in the
tallest chair at the table---really more of a golden throne---sat a wizened and
bespectacled ancient, with a silver-white beard that looked like it would go
almost to the floor if it were visible, watching over the Sorting with a
benevolent expression; as stereotypical in appearance as a Wise Old Man could
possibly be, without actually being Oriental. (Though Harry had learned to be
wary of stereotypical appearances from the first time he'd met Professor
McGonagall and thought that she ought to cackle.) The ancient wizard had
applauded every student Sorted, with an unwavering smile that somehow seemed
freshly delighted for each.

To the golden throne's left side was a man with sharp eyes and a dour face who
had applauded no-one, and who somehow managed to be looking straight back at
Harry every time Harry looked at him. Further to the left, the pale-faced man
Harry had seen in the Leaky Cauldron, whose eyes darted around as though in
panic at the surrounding crowd, and who seemed to occasionally jerk and twitch
in his seat; for some reason Harry kept finding himself staring at him. To that
man's left, a string of three older witches who didn't seem much interested in
the students. Then to the right side of the tall golden chair, a round-faced
middle-aged witch with a yellow hat, who had applauded every student except the
Slytherins. A tiny man standing on his chair, with a poofy white beard, who had
applauded every student, but smiled only upon the Ravenclaws. And on the
farthest right, occupying the same space as three lesser beings, the
mountainous entity who'd greeted them all after they'd disembarked from the
train, naming himself Hagrid, Keeper of Keys and Grounds.

"Is the man standing on his chair the Head of Ravenclaw?" Harry whispered
towards Hermione.

For once Hermione didn't answer this instantly; she was shifting constantly
from side to side, staring at the Sorting Hat, and fidgeting so energetically
that Harry thought her feet might be leaving the floor.

"Yes, he is," said one of the prefects who'd accompanied them, a young woman
wearing the blue of Ravenclaw. Miss Clearwater, if Harry recalled correctly.
Her voice was quiet, but conveyed a tinge of pride. "That is the Charms
Professor of Hogwarts, Filius Flitwick, the most knowledgeable Charms Master
alive, and a past Duelling Champion---"

"Why's he so \emph{short?}" hissed a student whose name Harry didn't recall.
"Is he a \emph{halfbreed?}"

A chill glance from the young lady prefect. "The Professor does indeed have
goblin ancestry---"

"What?" Harry said involuntarily, causing Hermione and four other students to
hush him.

Now Harry was getting a surprisingly intimidating glare from the Ravenclaw
prefect.

"I mean---" Harry whispered. "Not that I have a \emph{problem} with that---it's
just---I mean---how's that \emph{possible?} You can't just mix two different
species together and get viable offspring! It ought to scramble the genetic
instructions for every organ that's different between the two species---it'd be
like trying to build," they didn't have cars so he couldn't use a
scrambled-engine-blueprints analogy, "a half-carriage half-boat or
something{\ldots}"

The Ravenclaw prefect was still looking at Harry severely. "Why \emph{couldn't}
you have a half-carriage half-boat?"

"\emph{Hssh!}" hsshed another prefect, though the Ravenclaw witch had still
spoken quietly.

"I mean---" Harry said even more quietly, trying to figure out how to ask
whether goblins had evolved from humans, or evolved from a common ancestor of
humans like \emph{Homo erectus}, or if goblins had been \emph{made} out of
humans somehow---if, say, they were still genetically human under a heritable
enchantment whose magical effect was diluted if only one parent was a `goblin',
which would explain how interbreeding was possible, and in which case goblins
would \emph{not} be an incredibly valuable second data point for how
intelligence had evolved in other species besides \emph{Homo sapiens}---now
that Harry thought about it, the goblins in Gringotts \emph{hadn't} seemed very
much like genuinely alien, nonhuman intelligences, nothing like Dirdir or
Puppeteers---"I mean, where did goblins \emph{come} from, anyway?"

"Lithuania," Hermione whispered absently, her eyes still fixed firmly on the
Sorting Hat.

Now Hermione was getting a smile from the lady prefect.

"Never mind," whispered Harry.

At the lectern, Professor McGonagall called out, "Goldstein, Anthony!"

"RAVENCLAW!"

Hermione, next to Harry, was bouncing on her tiptoes so hard that her feet were
actually leaving the ground on each bounce.

"Goyle, Gregory!"

There was a long, tense moment of silence under the Hat. Almost a minute.

"SLYTHERIN!"

"Granger, Hermione!"

Hermione broke loose and ran full tilt towards the Sorting Hat, picked it up
and jammed the patchy old clothwork down hard over her head, making Harry
wince. Hermione had been the one to explain to \emph{him} about the Sorting
Hat, but she certainly didn't \emph{treat} it like an irreplaceable, vitally
important, 800-year-old artefact of forgotten magic that was about to perform
intricate telepathy on her mind and didn't seem to be in very good physical
condition.

"RAVENCLAW!"

And talk about your foregone conclusions. Harry didn't see why Hermione had
been so tense about it. In what weird alternative universe would that girl
\emph{not} be Sorted into Ravenclaw? If Hermione Granger didn't go to Ravenclaw
then there was no good reason for Ravenclaw House to exist.

Hermione arrived at the Ravenclaw table and got a dutiful cheer; Harry wondered
whether the cheer would have been louder, or quieter, if they'd had any idea
just what level of competition they'd welcomed to their table. Harry knew pi to
3.141592 because accuracy to one part in a million was enough for most
practical purposes. Hermione knew one hundred digits of pi because that was how
many digits had been printed in the back of her maths textbook.

Neville Longbottom went to Hufflepuff, Harry was glad to see. If that House
really did contain the loyalty and camaraderie it was supposed to exemplify,
then a Houseful of reliable friends would do Neville a whole world of good.
Clever kids in Ravenclaw, evil kids in Slytherin, wannabe heroes in Gryffindor,
and everyone who does the actual work in Hufflepuff.

(Though Harry \emph{had} been right to consult a Ravenclaw prefect first. The
young woman hadn't even looked up from her reading or identified Harry, just
jabbed a wand in Neville's direction and muttered something. After which
Neville had acquired a dazed expression and wandered off to the fifth carriage
from the front and the fourth compartment on the left, which indeed had
contained his toad.)

"Malfoy, Draco!" went to Slytherin, and Harry breathed a small sigh of relief.
It had \emph{seemed} like a sure thing, but you never did know what tiny event
might upset the course of your master plan.

Professor McGonagall called "Perks, Sally-Anne!", and from the gathered
children detached a pale waifish girl who looked oddly ethereal---like she
might mysteriously disappear the moment you stopped looking at her, and never
be seen again or even remembered.

And over at the Gryffindor table, there was a whispered conversation.

"\emph{What if he doesn't like it?}"

"\emph{He's got no right to not like it---}"

"\emph{---not after the prank he played on---}"

"\emph{---Neville Longbottom, his name was---}"

"\emph{---he's as fair a fair target now as fair can be.}"

"\emph{All right. Just make sure you don't forget your parts.}"

"\emph{We've rehearsed it often enough---}"

"\emph{---over the last three hours.}"

And Minerva McGonagall, from where she stood at the speaker's podium of the
Head Table, looked down at the next name on her list. \emph{Please don't let
him be a Gryffindor please don't let him be a Gryffindor OH PLEASE don't let
him be a Gryffindor{\ldots}} She took a deep breath, and called:

"Potter, Harry!"

There was a sudden silence in the hall as all whispered conversation stopped.

A silence broken by a horrible buzzing noise that modulated and changed in
hideous mockery of musical melody.

Minerva's head jerked around, shocked, and identified the buzzing noise as
coming from the Gryffindor direction, where They were \emph{standing on top of
the table} blowing into some kind of tiny devices held against Their lips. Her
hand started to drop to her wand, to \emph{Silencio} the lot of Them, but
another sound stopped her.

Dumbledore was chuckling.

Minerva's eyes went back to Harry Potter, who had only just started to step out
of line before he'd stumbled and halted.

Then the young boy began to walk again, moving his legs in odd sweeping
motions, and waving his arms back and forth and snapping his fingers, in
synchrony with Their music.

\begin{center}
\emph{To the tune of ``Ghostbusters''}

\emph{(As performed on the kazoo by Fred and George Weasley,
and sung by Lee Jordan.)}

.

\emph{There's a Dark Lord near?\\
Got no need to fear\\
Who you gonna call?}
\end{center}

"\shout{Harry Potter}!" shouted Lee Jordan, and the Weasley twins performed a
triumphant chorus.

\begin{center}
\emph{With a Killing Curse?\\
Well it could be worse.\\
Who you gonna call?}
\end{center}

"\shout{Harry Potter}!" There were a lot more voices shouting it this time.

The Weasley Horrors went off into an extended wailing, now accompanied by some
of the older Muggleborns, who had produced their own tiny devices, Transfigured
out of the school silverware no doubt. As their music reached its anticlimax,
Harry Potter shouted:

\begin{center}
\emph{I ain't afraid of Dark Lords!}
\end{center}

There was cheering then, especially from the Gryffindor table, and more
students produced their own antimusical instruments. The hideous buzzings
redoubled in volume and built to another awful crescendo:

\begin{center}
\emph{I ain't afraid of Dark Lords!}
\end{center}

Minerva glanced to both sides of the Head Table, afraid to look but with all
too good a notion of what she would see.

Trelawney frantically fanning herself, Flitwick looking on with curiosity,
Hagrid clapping along to the music, Sprout looking severe, and Quirrell gazing
at the boy with sardonic amusement. Directly to her left, Dumbledore humming
along; and directly to her right, Snape gripping his empty wine goblet,
white-knuckled, so hard that the thick silver was slowly deforming.

\begin{center}
\emph{Dark robes and a mask?\\
Impossible task?\\
Who you gonna call?\\
\shout{Harry Potter}!}

\emph{Giant Fire-Ape?\\
Old bat in a cape?\\
Who you gonna call?\\
\shout{Harry Potter}!}
\end{center}

Minerva's lips set in a white line. She would have words with Them about that
last verse, if They thought she was powerless because it was the first day of
school and Gryffindor had no points to take away. If They didn't care about
detentions then she would find something else.

Then, with a sudden gasp of horror, she looked in Snape's direction,
\emph{surely} he realised the Potter boy must have no idea who that was talking
about---

Snape's face had gone beyond rage into a kind of pleasant indifference. A faint
smile played about his lips. He was looking in the direction of Harry Potter,
not the Gryffindor table, and his hands held the crumpled remains of a former
wine goblet{\ldots}

And Harry walked forwards, sweeping his arms and legs through the motions of
the Ghostbusters dance, keeping a smile on his face. It was a great setup, had
caught him completely by surprise. The least he could do was play along and not
ruin it all.

Everyone was cheering him. It made him feel all warm inside and sort of awful
at the same time.

They were cheering him for a job he'd done when he was one year old. A job he
hadn't really finished. Somewhere, somehow, the Dark Lord was still alive.
Would they have been cheering quite so hard, if they knew that?

But the Dark Lord's power \emph{had} been broken once.

And Harry would protect them again. If there was in fact a prophecy and that
was what it said. Well, actually regardless of what any darn prophecy said.

All those people believing in him and cheering him---Harry couldn't stand to
let that be false. To flash and fade like so many other child prodigies. To be
a disappointment. To fail to live up to his reputation as a symbol of the
Light, never mind \emph{how} he'd gotten it. He would absolutely, positively,
no matter how long it took and even if it killed him, fulfill their
expectations. And then go on to \emph{exceed} those expectations, so that
people wondered, looking back, that they had once asked so little of him.

And he shouted out the lie that he'd invented because it scanned well and the
song called for it:

\begin{center}
\emph{I ain't afraid of Dark Lords!\\
I ain't afraid of Dark Lords!}
\end{center}

Harry took his last steps toward the Sorting Hat as the music ended. He swept a
bow to the Order of Chaos at the Gryffindor table, and then turned and swept
another bow to the other side of the hall, and waited for the applause and
giggling to die away{\ldots}

(In the back of his mind, he wondered if the Sorting Hat was genuinely
\emph{conscious} in the sense of being aware of its own awareness, and if so,
whether it was satisfied with only getting to talk to eleven-year-olds once per
year. Its song had implied so: \emph{Oh, I'm the Sorting Hat and I'm okay, I
sleep all year and I work one day{\ldots}})

When there was once more silence in the room, Harry sat on the stool and
\emph{carefully} placed onto his head the 800-year-old telepathic artefact of
forgotten magic.

Thinking, just as hard as he could: \emph{Don't Sort me yet! I have questions I
need to ask you! Have I ever been Obliviated? Did you Sort the Dark Lord when
he was a child and can you tell me about his weaknesses? Can you tell me why I
got the brother wand to the Dark Lord's? Is the Dark Lord's ghost bound to my
scar and is that why I get so angry sometimes? Those are the most important
questions, but if you've got another moment can you tell me anything about how
to rediscover the lost magics that created you?}

Into the silence of Harry's spirit, where before there had never been any voice
but one, there came a second and unfamiliar voice, sounding distinctly worried:

"\emph{Oh, dear. This has never happened before{\ldots}}"
